Tertiary analyses (scale construction)

### 2025-07-17 analysis/tertiary_analyses.qmd
update presentation in tertiary_analyses

### Item total correlations

```{r}
neg_items <- c("A_13", "A_14", "A_21",
  "KGr_35", "KGr_36", "KGr_37", "KGr_38", "KGr_39", "KGr_40", "KGr_41", "KGr_43",
  "KGe_52", "KGe_53", "KGe_54", "KGe_55", "KGe_56", "KGe_57", "KGe_58")
dat_pilot_recode <- dat_pilot |> 
  select(KGr_22:KGr_40) |>
  mutate(across(all_of(neg_items), ~ 7 - .))

rel_age <- psych::alpha(dat_pilot_recode |> select(starts_with("A")))
rel_height <- psych::alpha(dat_pilot_recode |> select(starts_with("KGr")))
rel_weight <- psych::alpha(dat_pilot_recode |> select(starts_with("KGe")))
```

@@

```{r}
rel_age$item.stats
rel_height$item.stats
rel_weight$item.stats
```

>>>>

### Reliability estimates and item total correlations

```{r}
neg_items <- c("A_13", "A_14", "A_21",
  "KGr_35", "KGr_36", "KGr_37", "KGr_38", "KGr_39", "KGr_40", "KGr_41", "KGr_43",
  "KGe_52", "KGe_53", "KGe_54", "KGe_55", "KGe_56", "KGe_57", "KGe_58")
dat_pilot_recode <- dat_pilot |> 
  select(KGr_22:KGr_40) |>
  mutate(across(all_of(neg_items), ~ 7 - .))
```

```{r}
rel_age <- psych::alpha(dat_pilot_recode |> select(starts_with("A")))
rel_height <- psych::alpha(dat_pilot_recode |> select(starts_with("KGr")))
rel_weight <- psych::alpha(dat_pilot_recode |> select(starts_with("KGe")))
```

@@

```{r}
rel_age
rel_height
rel_weight
```
